Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/paper_draft4.Rmd
moved text on initial prior to come before introduction of power prior
add sentence to clarify bias
fixed minor error in reference to Rstan

To evaluate the proposed method, we conducted a simulation study using Stan 2.261, a Hamiltonian Monte Carlo engine for Bayesian inference by way of R version 4.2.2 and RStan and RStan [@rstan]. These simulations primarily show how much the size of the historical data affects our ability to detect bias and how much the power prior discounted the weight of the historical data. As introduced above, $b > 0$ represents a prosecutor's bias against a prospective juror within the cognizable class, while $b = 0$ denotes no bias. For simplicity, we assume the defense attorney has no bias.

>>>>

To evaluate the proposed method, we conducted a simulation study using Stan 2.261, a Hamiltonian Monte Carlo engine for Bayesian inference by way of R version 4.2.2 and RStan [@rstan]. These simulations primarily show how much the size of the historical data affects our ability to detect bias and how much the power prior discounted the weight of the historical data. As introduced above, $b > 0$ represents a prosecutor's bias against a prospective juror within the cognizable class, while $b = 0$ denotes no bias. For simplicity, we assume the defense attorney has no bias.
